Note on: Out-of-Sample Error for Laplacian Eigenmaps

### 2021-03-27 notes/weekly_notes/12.24.20.NotesForWeek.tex
Completed proof regarding bias of kernel smoothing.

The estimated function $\wh{f}$ we will consider is a kernel smoother passed over $\wh{\theta}$,
\begin{equation}
\label{eqn:kernel_smoother_laplacian_eigenmaps}
\wh{f}(x) := T_{\varepsilon,n}\wh{\theta}_{1:n}(x).
\end{equation}
In order to relate the out-of-sample error $\|\wh{f} - f^{\ast}\|_P$ to the in-sample error $\|\wh{\theta}_{1:n} - f^{\ast}_{1:n}\|_n$, we will assume the following.
\begin{enumerate}[label=(A\arabic*)]
	\item
	\label{asmp:kernel}
	The kernel function $\eta$ is compactly supported on a subset of $[0,1]$. Additionally, $\eta$ is Lipschitz on its support. Finally, for convenience we will assume that $\eta$ is normalized, 
	\begin{equation*}
	\int_{0}^{\infty} \eta(s) \,ds = 1.
	\end{equation*}
	\item 
	\label{asmp:domain} There exists $\alpha > 0$ such that for every $x \in \mc{X}$, $d_{\nu}(x) \geq \alpha \cdot \varepsilon^d$.
	\item 
	\label{asmp:density}The distribution $P$ admits a density $p$ with respect to Lebesgue measure. The density $p \in C^1(\mc{X})$, and is bounded away from $0$ and $\infty$ for all $x \in \mc{X}$,
	\begin{equation*}
	0 < p_{\min} \leq p(x) < p_{\max} < \infty.
	\end{equation*}
\end{enumerate}
Under Assumption~\ref{asmp:kernel}, we automatically have that $d_\nu(x) = \varepsilon^d$ for all $x \in \mc{X}_{\varepsilon}$. Assumption~\ref{asmp:domain} is thus a condition on the boundary $\partial \Omega$, and is implied for all sufficiently small $\varepsilon$ if the boundary is Lipschitz. Denoting $K(\cdot) = (\eta(\cdot))^2$, we note that Assumption~\ref{asmp:kernel} implies that $\eta$ is square-integrable, $\int_{0}^{\infty} K(s) \,ds < \infty$.
\begin{lemma}
	\label{lem:kernel_smoothing_laplacian_eigenmaps}
	Suppose $f^{\ast} \in H^1(\mc{X})$ and $p \in C^1(\mc{X})$. Then with probability at least $1 - \delta - C\varepsilon^d\exp\{-Cn\varepsilon^d\}$, it holds that
	\begin{equation*}
	\|\wh{f} - f^{\ast}\|_P^2 \leq C\biggl(\|\wh{\theta}_{1:n} - f^{\ast}_{1:n}\|_n^2 + \frac{1}{\delta} \cdot \frac{\varepsilon^2}{n\varepsilon^d} |f|_{H^1(\mc{X})}^2 + \frac{1}{\delta}\|T_{\varepsilon,P}f^{\ast} - f^{\ast}\|_P^2\biggr)
	\end{equation*}
\end{lemma}
Notice that the variance term in the above is smaller than the typical variance term for kernel smoothing of noisy data (on the order of $1/(n\varepsilon^d)$) by a factor of $\varepsilon^2$. The bias term, on the other hand, is standard (at least when $f^{\ast} \in C_0^s(\Omega)$). In particular the following estimate of the bias can be obtained. 
\begin{lemma}
	\label{lem:kernel_smoothing_bias}
	Suppose $f^{\ast} \in H_0^{s}(\Omega)$, $p \in C^{r}(\Omega)$ for $r = s - 1$, and that $\eta$ is an order-$s$ kernel. It follows that
	\begin{equation*}
	\|T_{\varepsilon,P}f^{\ast} - f^{\ast}\|_P^2 \leq C \varepsilon^{2s}.
	\end{equation*}
\end{lemma}
\begin{proof}[Proof (when dimension $d = 1$).]
	\textcolor{red}{(TODO)}
\end{proof}

@@

\section{Proof of Lemma~\ref{lem:kernel_smoothing_bias}}
Letting $\Omega_{\varepsilon} = \{x: B(x,\varepsilon) \subset \Omega\}$ and $\partial_{\varepsilon}\Omega = \Omega \setminus \Omega_{\varepsilon}$, we have that 
\begin{equation*}
\|L_{P,\varepsilon}u\|_P^2 = \underbrace{\int_{\Omega_{\varepsilon}} \bigl(L_{\varepsilon,P}u(x)\bigr)^2 \,dP(x)}_{:=I_1} + \underbrace{\int_{\partial_{\varepsilon}\Omega} \bigl(L_{\varepsilon,P}u(x)\bigr)^2 \,dP(x)}_{:=I_2}
\end{equation*}
We will separately upper bound $I_1$---using the higher order property of $\eta$---and $I_2$---using the zero-trace property of $u$ and its $1$st up through $j - 1$st order derivatives.

\paragraph{Upper bound on $I_1$.}

\paragraph{Upper bound on $I_2$.}

>>>>

The estimated function $\wh{f}$ we will consider is a kernel smoother passed over $\wh{\theta}$,
\begin{equation}
\label{eqn:kernel_smoother_laplacian_eigenmaps}
\wh{f}(x) := T_{\varepsilon,n}\wh{\theta}_{1:n}(x).
\end{equation}
In order to relate the out-of-sample error $\|\wh{f} - f^{\ast}\|_P$ to the in-sample error $\|\wh{\theta}_{1:n} - f^{\ast}_{1:n}\|_n$, we will assume the following.
\begin{enumerate}[label=(A\arabic*)]
	\item
	\label{asmp:kernel}
	The kernel function $\eta$ is compactly supported on a subset of $[0,1]$. Additionally, $\eta$ is Lipschitz on its support. Finally, for convenience we will assume that $\eta$ is normalized, 
	\begin{equation*}
	\int_{0}^{\infty} \eta(s) \,ds = 1.
	\end{equation*}
	\item 
	\label{asmp:domain} There exists $\alpha > 0$ such that for every $x \in \mc{X}$, $d_{\nu}(x) \geq \alpha \cdot \varepsilon^d$.
	\item 
	\label{asmp:density}The distribution $P$ admits a density $p$ with respect to Lebesgue measure. The density $p \in C^1(\mc{X})$, and is bounded away from $0$ and $\infty$ for all $x \in \mc{X}$,
	\begin{equation*}
	0 < p_{\min} \leq p(x) < p_{\max} < \infty.
	\end{equation*}
\end{enumerate}
Under Assumption~\ref{asmp:kernel}, we automatically have that $d_\nu(x) = \varepsilon^d$ for all $x \in \mc{X}_{\varepsilon}$. Assumption~\ref{asmp:domain} is thus a condition on the boundary $\partial \Omega$, and is implied for all sufficiently small $\varepsilon$ if the boundary is Lipschitz. Denoting $K(\cdot) = (\eta(\cdot))^2$, we note that Assumption~\ref{asmp:kernel} implies that $\eta$ is square-integrable, $\int_{0}^{\infty} K(s) \,ds < \infty$.
\begin{lemma}
	\label{lem:kernel_smoothing_laplacian_eigenmaps}
	Suppose $f^{\ast} \in H^1(\mc{X})$ and $p \in C^1(\mc{X})$. Then with probability at least $1 - \delta - C\varepsilon^d\exp\{-Cn\varepsilon^d\}$, it holds that
	\begin{equation*}
	\|\wh{f} - f^{\ast}\|_P^2 \leq C\biggl(\|\wh{\theta}_{1:n} - f^{\ast}_{1:n}\|_n^2 + \frac{1}{\delta} \cdot \frac{\varepsilon^2}{n\varepsilon^d} |f|_{H^1(\mc{X})}^2 + \frac{1}{\delta}\|T_{\varepsilon,P}f^{\ast} - f^{\ast}\|_P^2\biggr)
	\end{equation*}
\end{lemma}
Notice that the variance term in the above is smaller than the typical variance term for kernel smoothing of noisy data (on the order of $1/(n\varepsilon^d)$) by a factor of $\varepsilon^2$. The bias term, on the other hand, is standard (at least when $f^{\ast} \in C_0^s(\Omega)$). In particular the following estimate of the bias can be obtained. 
\begin{lemma}
	\label{lem:kernel_smoothing_bias}
	Suppose $f^{\ast} \in H_0^{s}(\Omega)$, $p \in C^{r}(\Omega)$ for $r = s - 1$, and that $\eta$ is an order-$s$ kernel. It follows that
	\begin{equation*}
	\|T_{\varepsilon,P}f^{\ast} - f^{\ast}\|_P^2 \leq C \varepsilon^{2s}.
	\end{equation*}
\end{lemma}
For the proof of this claim see Section~\ref{sec:kernel_smoothing_bias_pf}.

@@

\section{Proof of Lemma~\ref{lem:kernel_smoothing_bias}}
\label{sec:kernel_smoothing_bias_pf}
Letting $\Omega_{\varepsilon} = \{x: B(x,\varepsilon) \subset \Omega\}$ and $\partial_{\varepsilon}\Omega = \Omega \setminus \Omega_{\varepsilon}$, we have that 
\begin{equation*}
\|L_{P,\varepsilon}u\|_P^2 = \underbrace{\int_{\Omega_{\varepsilon}} \bigl(L_{P,\varepsilon}u(x)\bigr)^2 \,dP(x)}_{:=I_1} + \underbrace{\int_{\partial_{\varepsilon}\Omega} \bigl(L_{\varepsilon,P}u(x)\bigr)^2 \,dP(x)}_{:=I_2}
\end{equation*}
We will separately upper bound $I_1$---using the higher order property of $\eta$---and $I_2$---using the zero-trace property of $u$ and its $1$st up through $(j - 1)$st order derivatives.

\subsection{Upper bound on $I_1$.}
\paragraph{Taylor expansions, and relevant facts.}
Suppose $x \in \mc{X}_{\varepsilon}$ and $x' \in B(x,\varepsilon)$. We take a Taylor expansion of $u(x')$ around $x' = x$,
\begin{equation*}
u(x') - u(x) = \sum_{j = 1}^{s - 1} \frac{1}{j!}\bigl(d_x^{j}u\bigr)(x' - x) + r_{x'}^{s}(x;u)
\end{equation*}
We likewise take an order $k$ Taylor expansion of $p(x')$ around $x'  = x$ (where $k = 1$ if $s = 1$, and otherwise $k = s - 1$,)
\begin{equation*}
p(x') = p(x) + \sum_{j = 1}^{k - 1}\frac{1}{j!}\bigl(d_x^{j}p\bigr)(x' - x) + r_{x'}^{k}(x;p).
\end{equation*}
Here for a given $z \in \Rd$ and $j$-times differentiable function $f: \mc{X} \to \Reals$, we use the notation $\bigl(d_x^jf\bigr)(z) := \sum_{\abs{\alpha} = j} D^{\alpha}f(x) z^{\alpha}$. The remainder term $r_{x'}$ is given by
\begin{equation*}
r_{x'}^j(x;f) = \frac{1}{(j - 1)!} \int_{0}^{1}(1 - t)^{j - 1} \bigl(d_{x + t(x' - x)}^{j}f\bigr)(x' - x) \,dt,
\end{equation*}
where we note that $x + t(x' - x) \in B(x,\varepsilon) \subseteq \mc{X}$. Finally, we have adopted the convention that $\sum_{j = 1}^{0} a_j = 0$.

We now recall some standard facts regarding Taylor expansions. First, remember that that $\bigl(d_x^{j}f\bigr)(z)$ is a degree-$j$ polynomial---and thus a $j$-homogeneous function---in $z$. On the other hand, for any degree-$j$ polynomial $q_j(z)$ and order-$s$ kernel $\eta$, if $j < s$ by converting to polar coordinates we can verify that
\begin{equation*}
\int_{B(0,1)} q_j(z) \eta(\|z\|) \,dz = 0.
\end{equation*}
We now give estimates on the remainder term in both sup-norm and $L^2(\mc{X}_{\varepsilon})$ norm, each of which hold for any $z \in B(0,1)$. In sup-norm, we have that 
\begin{equation*}
\sup_{x \in \mc{X}_{\varepsilon}}|r_{x + \varepsilon z}^j(x;f)| \leq C \varepsilon^j \|f\|_{C^j(\mc{X})},
\end{equation*}
whereas in $L^2(\mc{X}_{\varepsilon})$ norm we have,
\begin{equation}
\label{eqn:sobolev_remainder_term}
\int_{\mc{X}_{\varepsilon}} \bigl|r_{x + t \varepsilon z}^j(x;f)\bigr|^2 \,dx \leq \varepsilon^{2j} \int_{\mc{X}_{\varepsilon}} \int_{0}^{1} |d_{x + t\varepsilon z}^jf(z)|^2 \,dt \,dx \leq \varepsilon^{2j} \|d^jf\|_{\Leb^2(\mc{X})}^2.
\end{equation}

\paragraph{Upper bound on $I_1$.}
Taking a Taylor expansion of $u(x')$ around $x' = x$, we see that
\begin{equation*}
d_P(x) \cdot L_{P,\varepsilon}u(x) = \sum_{j = 1}^{s - 1} \int \bigl(d_x^ju\bigr)(x' - x) \eta\biggl(\frac{\|x' - x\|}{\varepsilon}\biggr) \,dP(x') + \int r_{x'}^j(x;u) \eta\biggl(\frac{\|x' - x\|}{\varepsilon}\biggr) \,dP(x')
\end{equation*}
Next we take a Taylor expansion of $p(x')$ around $x' = x$ and represent $L_{P,\varepsilon}u(x)$ as the sum of three terms,
\begin{equation}
\label{pf:kernel_smoothing_bias_1}
\begin{aligned}
d_P(x) \cdot L_{P,\varepsilon}u(x) & = \sum_{j_1 = 1}^{s - 1} \sum_{j_2 = 0}^{k - 1} \int \bigl(d_x^{j_1}u\bigr)(x' - x) \bigl(d_x^{j_2}p\bigr)(x' - x) \eta\biggl(\frac{\|x' - x\|}{\varepsilon}\biggr) \,dx' \quad + \\
& \quad \sum_{j = 1}^{s - 1} \int \bigl(d_x^ju\bigr)(x' - x)  r_{x'}^{k}(x;p) \eta\biggl(\frac{\|x' - x\|}{\varepsilon}\biggr) \,dx' \quad  + \\
& \quad \int r_{x'}^j(x;u) \eta\biggl(\frac{\|x' - x\|}{\varepsilon}\biggr) \,dP(x') \\
& := J_1(x) + J_2(x) + J_3(x).
\end{aligned}
\end{equation}
Note immediately that by Assumption~\ref{asmp:density}, we have that $\inf_{x \in \mc{X}_{\varepsilon}}|d_{P}(x)| \geq p_{\min} \varepsilon^d.$ We will additionally show that for each of $m = 1,2,3$, 
\begin{equation*}
\int_{\Omega_{\varepsilon}} |J_m(x)|^2 \,dP(x) \leq C \varepsilon^{2(s + d)} \|u\|_{H^s(\mc{X})}^2,
\end{equation*}
for a constant $C$ that does not depend on $u$. Plugging these bounds back into~\eqref{pf:kernel_smoothing_bias_1} will imply that
\begin{equation*}
I_1 \leq C \varepsilon^{2s} \|u\|_{H^s(\mc{X})}^2.
\end{equation*}

\underline{\textit{Upper bound on $J_1(x)$}}.
Recalling that $d_x^jf(\cdot)$ is a $j$-homogeneous function, we have that
\begin{align*}
J_1(x) & = \sum_{j_1 = 1}^{s - 1} \sum_{j_2 = 0}^{k - 1} \int_{\mc{X}} \bigl(d_x^{j_1}u\bigr)(x' - x) \cdot \bigl(d_x^{j_2}p\bigr)(x' - x) \cdot \eta\biggl(\frac{\|x' - x\|}{\varepsilon}\biggr) \,dx' \\
& = \varepsilon^d \sum_{j_1 = 1}^{s - 1} \sum_{j_2 = 0}^{k - 1} \int_{B(0,1)} \bigl(d_{x }^{j_1}u\bigr)(\varepsilon z) \cdot \bigl(d_{x}^{j_2}p\bigr)(\varepsilon z) \cdot \eta\bigl(\|z\|\bigr) \,dz \\
& = \varepsilon^d \sum_{j_1 = 1}^{s - 1} \sum_{j_2 = 0}^{k - 1} \varepsilon^{j_1 + j_2} \int_{B(0,1)} \bigl(d_{x}^{j_1}u\bigr)(z) \cdot \bigl(d_{x}^{j_2}p\bigr)(z) \cdot \eta\bigl(\|z\|\bigr) \,dz.
\end{align*}
Noting $d_{x}^{j_1}u \cdot d_x^{j_2}p$ is a degree $j_1 + j_2$ polynomial, we note that for all terms in the above sum such that $j_1 + j_2 < s$,
\begin{equation*}
\int_{B(0,1)} \bigl(d_{x}^{j_1}u\bigr)(z) \cdot \bigl(d_{x}^{j_2}p\bigr)(z) \cdot \eta\bigl(\|z\|\bigr) \,dx' = 0.
\end{equation*}
On the other hand if $j_1 + j_2 \geq s$, we have that
\begin{align*}
\biggl|\int_{B(0,1)} \bigl(d_{x}^{j_1}u\bigr)(z) \cdot \bigl(d_{x}^{j_2}p\bigr)(z) \cdot \eta\bigl(\|z\|\bigr) \,dz\biggr| \leq \|d^jp\|_{L^{\infty}} \int_{B(0,1)} \Bigl|\bigl(d_x^{j}u\bigr)(z)\Bigr| \cdot \Bigl|\eta(\|z\|)\Bigr| \,dz.  
\end{align*}
Consequently, applying these bounds for each $x \in \mc{X}_{\varepsilon}$ and integrating, we obtain
\begin{align*}
\int |J_1(x)|^2 \,dP(x) & \leq C \varepsilon^{2(s + d)} \|p\|_{C^k(\mc{X})} \sum_{j = 1}^{s - 1}  \int_{\mc{X}_{\varepsilon}} \biggl(\int_{B(0,1)} \Bigl|\bigl(d_x^{j}u\bigr)(z)\Bigr| \cdot \Bigl|\eta(\|z\|)\Bigr| \,dz\biggr)^2 \,dx \\
& \leq C \varepsilon^{2(s + d)} \|p\|_{C^k(\mc{X})} \sum_{j = 1}^{s - 1} \|d_ju\|_{L^2(\mc{X}_{\varepsilon})}^2 \\
& \leq  C \varepsilon^{2(s + d)} \|p\|_{C^k(\mc{X})} \|u\|_{H^s(\mc{X})}^2,
\end{align*}
where we show the middle inequality in~\eqref{pf:kernel_smoothing_bias_3}, below.

\underline{\textit{Upper bound on $J_2(x)$}}.
Recalling that $|r_{x + z\varepsilon}^{k}(x; p)| \leq C\varepsilon^{k}\|p\|_{C^{k}(\mc{X})}$ for any $z \in B(0,1)$, and that $d_x^jf(\cdot)$ is a $j$-homogeneous function, we have that
\begin{align}
|J_2(x)| & \leq \sum_{j = 1}^{s - 1} \frac{1}{j!}\int \Bigl|\bigl(d_x^{j}u\bigr)(x' - x)\Bigr| \cdot \Bigl|r_{x'}^{k}(x;p)\Bigr| \cdot \biggl|\eta\biggl(\frac{\|x' - x\|}{\varepsilon}\biggr)\biggr| \,dx' \nonumber \\
& = \varepsilon^{d} \sum_{j = 1}^{s - 1} \frac{1}{j!}\int_{B(0,1)} \Bigl|\bigl(d_x^{j}u\bigr)(\varepsilon z)\Bigr| \cdot |r_{x + z\varepsilon}^{k}(x;p)| \cdot \Bigl|\eta(\|z\|)\Bigr| \,dz \nonumber \\
& \leq C\varepsilon^{k + 1 + d}\|p\|_{C^{k}(\mc{X})} \sum_{j = 1}^{s - 1} \frac{1}{j!} \int_{B(0,1)} \Bigl|\bigl(d_x^{j}u\bigr)(z)\Bigr| \cdot \Bigl|\eta(\|z\|)\Bigr| \,dz \label{pf:kernel_smoothing_bias_2}
\end{align}
Furthermore, for each $j = 1,\ldots,s - 1$ convolution of $d_x^ju$ with $\eta$ increases the $\Leb^2(\mc{X}_{\varepsilon})$ norm by at most a constant, meaning 
\begin{equation}
\label{pf:kernel_smoothing_bias_3}
\begin{aligned}
\int_{\mc{X}_{\varepsilon}} \biggl(\int_{B(0,1)} \Bigl|\bigl(d_x^{j}u\bigr)(z)\Bigr| \cdot \Bigl|\eta(\|z\|)\Bigr| \,dz\biggr)^2 \,dx & \leq \int_{\mc{X}_{\varepsilon}} \biggl(\int_{B(0,1)} \Bigl[\bigl(d_x^ju\bigr)(z)\Bigr]^2 \,dz \biggr) \cdot \biggl(\int_{B(0,1)} K(\|z\|) \,dz \biggr) \,dx \\
& \leq \|\eta\|_{\infty}^2  \int_{B(0,1)} \int_{\mc{X}_{\varepsilon}} \Bigl[\bigl(d_x^ju\bigr)(z)\Bigr]^2 \,dx \,dz \\
& \leq \|\eta\|_{\infty}^2 \nu_d \cdot \|d^ju\|_{\Leb^2(\mc{X_{\varepsilon}})}^2.
\end{aligned}
\end{equation}
Combining this with~\eqref{pf:kernel_smoothing_bias_2}, we conclude that
\begin{align*}
\int_{\mc{X}_{\varepsilon}} |J_2(x)|^2 \,dP(x) & \leq C p_{\max} \|p\|_{C^{k}(\mc{X})}^2 \varepsilon^{2(k + 1 + d)} \sum_{j = 1}^{s - 1} \biggl(\frac{1}{j!} \int_{B(0,1)} \Bigl|\bigl(d_x^{j}u\bigr)(z)\Bigr| \cdot \Bigl|\eta(\|z\|)\Bigr| \,dz\biggr) \\
& \leq  C p_{\max} \|p\|_{C^{k}(\mc{X})}^2 \|\eta\|_{\infty}^2 \nu_d \varepsilon^{2(k + 1 + d)} \sum_{j = 1}^{s - 1} \cdot \|d^ju\|_{\Leb^2(\mc{X_{\varepsilon}})}^2 \\
& \leq C \varepsilon^{2(k + 1 + d)} \|u\|_{H^s(\mc{X})}^2,
\end{align*}
whence the claim follows since by assumption either $k + 1 > s$ (when $s = 1$), or $k + 1 = s$ (when $s \geq 2$).

\underline{\textit{Upper bound on $J_3(x)$}}.
We begin with a pointwise upper bound on $|J_3(x)|$, 
\begin{align*}
|J_3(x)| & \leq p_{\max} \int_{\mc{X}} \bigl|r_{x'}^s(x;u)\bigr| \biggl|\eta\biggl(\frac{\|x' - x\|}{\varepsilon}\biggr)\biggr| \,dx' \\
& = p_{\max} \varepsilon^d \int_{B(0,1)} \bigl|r_{x + \varepsilon z}^s(x;u)\bigr| \bigl|\eta(\|z\|)\bigr| \,dz,
\end{align*}
and applying the Cauchy-Schwarz inequality, we deduce a pointwise upper bound on $|J_3(x)|^2$,
\begin{align*}
|J_3(x)|^2 & \leq p_{\max}^2 \varepsilon^{2d} \biggl(\int_{B(0,1)} \bigl|r_{x + \varepsilon z}^s(x;u)\bigr|^2 \,dz\biggr) \cdot \biggl(\int_{B(0,1)} \bigl|\eta(\|z\|)\bigr| \,dz\biggr) \\
& \leq p_{\max}^2 \|\eta\|_{\infty}^2 \nu_d \varepsilon^{2d}  \int_{B(0,1)} \bigl|r_{x + \varepsilon z}^s(x;u)\bigr|^2 \,dz.
\end{align*}
Applying this pointwise over all $x \in \mc{X}_{\varepsilon}$ and integrating, we obtain
\begin{align*}
\int_{\mc{X}_{\varepsilon}} |J_3(x)|^2 \,dP(x) & \leq p_{\max}^3 \|\eta\|_{\infty}^2 \nu_d \varepsilon^{2d} \int_{\mc{X}_{\varepsilon}} \int_{B(0,1)} \bigl|r_{x + \varepsilon z}^s(x;u)\bigr|^2 \,dz \\
& = p_{\max}^3 \|\eta\|_{\infty}^2 \nu_d \varepsilon^{2d} \int_{B(0,1)} \int_{\mc{X}_{\varepsilon}} \bigl|r_{x + \varepsilon z}^s(x;u)\bigr|^2 \,dz \\
& \leq p_{\max}^3 \|\eta\|_{\infty}^2 \nu_d^2 \varepsilon^{2(s + d)} \|d^sf\|_{L^2(\mc{X}_{\varepsilon})},
\end{align*}
with the last inequality following from~\eqref{eqn:sobolev_remainder_term}.

\paragraph{Upper bound on $I_2$.}
We begin by demonstrating that $I_2$ is upper bounded by $C\|u\|_{\Leb^2(\partial_{2\varepsilon}\mc{X})}^2$. Recall that by assumption $d_P(x) \geq \alpha p_{\min} \varepsilon^d$ for each $x \in \mc{X}$. On the other hand, at every $x \in \mc{X}$ we have that
\begin{align*}
\bigl|d_P(x) \cdot L_{P,\varepsilon}u(x)\bigr|^2 & \leq p_{\max}^2 \biggl[\int \Bigl(|u(x)|^2 + |u(x')|^2\Bigr) K^{1/2}\biggl(\frac{\|x' - x\|}{\varepsilon}\biggr) \,dx'\biggr] \cdot \biggl[\int K^{1/2}\biggl(\frac{\|x' - x|}{\varepsilon}\biggr) \,dx\biggr] \\
& \leq 2 p_{\max}^2 \|\eta\|_{\infty} \varepsilon^d \int \Bigl(|u(x)|^2 + |u(x')|^2\Bigr) K^{1/2}\biggl(\frac{\|x' - x\|}{\varepsilon}\biggr) \,dx'.
\end{align*}
It follows that
\begin{align*}
I_2 & = \int_{\partial_{\varepsilon}\mc{X}} \bigl|L_{P,\varepsilon}u(x)\bigr|^2 \,dP(x) \\
& \leq \frac{2p_{\max}^2 |\eta\|_{\infty}}{p_{\min}^2 \alpha \varepsilon^d} \int_{\partial_{\varepsilon}\mc{X}} \int_{\mc{X}} \Bigl(|u(x)|^2 + |u(x')|^2\Bigr) K^{1/2}\biggl(\frac{\|x' - x\|}{\varepsilon}\biggr) \,dx' \\ 
& \leq \frac{4p_{\max}^2 \|\eta\|_{\infty}^2}{p_{\min}^2 \alpha} \int_{\partial_{2\varepsilon}\mc{X}} |u(x)|^2 \,dx.
\end{align*}
We will now use the zero-trace property of $u$ to show that there exists a number $c$, which depends only on $\mc{X}$ such that for all $\varepsilon \leq c$,
\begin{equation}
\label{pf:kernel_smoothing_bias_5}
\int_{\partial_{\varepsilon}\mc{X}} |u(x)|^2 \,dx \leq C\varepsilon^{2s}.
\end{equation}
We will build to this result by a series of intermediate steps. Many of these steps are related to the proof of Theorem 18.1 in \textcolor{red}{(Leoni)}.

\underline{\textit{Step 1: Local Patch.}}
To begin, we assume that for some $c_0 > 0$ and a Lipschitz mapping $\phi: \Reals^{d - 1} \to [-c_0,c_0]$, we have that $u \in C_c^{\infty}(U_{\phi}(c_0))$, where 
\begin{equation*}
U_{\phi}(c_0) = \Bigl\{y \in Q(0,c_0): \phi(y_{-d}) \leq y_d\Bigr\}, 
\end{equation*}
and here $Q(0,c_0)$ is the $d$-dimensional cube of side length $c_0$, centered at $0$. We will show that for all $0 < \varepsilon < c_0$, and for the tubular neighborhood $V_{\phi}(\varepsilon) = \{y \in Q(0,c_0): \phi(y_{-d}) \leq y_d \leq \phi(y_{-d}) + \varepsilon\}$, we have that
\begin{equation*}
\int_{V_{\phi}(\varepsilon)} |u(x)|^2 \,dx \leq C\varepsilon^{2s} \|u\|_{H^s(U_{\phi}(c_0))}^2.
\end{equation*}
For a given $y = (y',y_d) \in V_{\phi}(\varepsilon)$, let $y_0 = (y',\phi(y'))$. Taking the Taylor expansion of $u(y)$ around $y = y_0$ because $u$ is compactly supported in $V_{\phi}$ it follows that,
\begin{align*}
u(y) & = u(y_0) + \sum_{j = 1}^{s - 1} \frac{1}{j!} D^{je_d}u(y_0) \bigl(y_d - \phi(y')\bigr)^j + \frac{1}{(s - 1)!}\int_{\phi(y')}^{y_d} (1 - t)^{s - 1} D^{se_d}u(y',z) \bigl(y_d - z\bigr)^{s - 1} \,dz \Longrightarrow\\
|u(y)| & \leq C\varepsilon^{s - 1}\int_{\phi(y')}^{y_d} \bigl|D^{se_d}u(y',z)\bigr| \,dz. 
\end{align*}
Consequently, by squaring both sides and applying Cauchy-Schwarz, we have that
\begin{equation*}
|u(y)|^2 \leq C\varepsilon^{2(s - 1)} \biggl(\int_{\phi(y')}^{y_d} \bigl|D^{se_d}u(y',z)\bigr| \,dz\biggr)^2 \leq C\varepsilon^{2s - 1} \int_{\phi(y')}^{y_d} \bigl|D^{se_d}u(y',z)\bigr|^2 \,dz.
\end{equation*}
Applying this bound for each $y \in V_{\phi}(\varepsilon)$, and then integrating, we obtain
\begin{align}
\int_{V_{\phi}(\varepsilon)} |u(y)|^2 \,dy & \leq \int_{Q_{d - 1}(c_0)} \int_{\phi(y')}^{\phi(y') + \varepsilon} |u(y',y_d)|^2 \,dy_d \,dy' \nonumber \\
& \leq C\varepsilon^{2s - 1}\int_{Q_{d - 1}(c_0)}  \int_{\phi(y')}^{\phi(y') + \varepsilon} \int_{\phi(y')}^{y_d} \bigl|D^{se_d}u(y',z)\bigr|^2 \,dz \,dy_d \,dy' \label{pf:kernel_smoothing_bias_4}
\end{align}
where we have written $Q_{d - 1}(0,c_0)$ for the $d - 1$ dimensional cube of side length $c_0$, centered at $0$. Exchanging the order of the inner two integrals then gives
\begin{align*}
\int_{\phi(y')}^{\phi(y') + \varepsilon} \int_{\phi(y')}^{y_d} \bigl|D^{se_d}u(y',z)\bigr|^2 \,dz \,dy_d & = \int_{\phi(y')}^{\phi(y') + \varepsilon} \int_{z}^{\varepsilon} \bigl|D^{se_d}u(y',z)\bigr|^2 \,dy_d \,dz \\
& \leq C \varepsilon \int_{\phi(y')}^{\phi(y') + \varepsilon} \bigl|D^{se_d}u(y',z)\bigr|^2 \,dz \\
& \leq C \varepsilon \int_{\phi(y')}^{c_0} \bigl|D^{se_d}u(y',z)\bigr|^2 \,dz.
\end{align*}
Finally, plugging back into~\eqref{pf:kernel_smoothing_bias_4}, we conclude that
\begin{equation*}
\int_{V_{\phi}(\varepsilon)} |u(y)|^2 \,dy \leq C \varepsilon^{2s} \int_{Q_{d - 1}(0,c_0)} \int_{\phi(y')}^{c_0} \bigl|D^{se_d}u(y',z)\bigr|^2 \,dz \,dy' \leq C \varepsilon^{2s} |u|_{H^s(U_{\phi}(c_0))}^2.
\end{equation*}

\underline{\textit{Step 2: Rigid motion of local patch.}} Now, suppose that at a point $x_0 \in \partial \mc{X}$, there exists a rigid motion $T: \Rd \to \Rd$ for which $T(x_0) = 0$, and a number $C_0$ such that for all $\varepsilon \cdot C_0 \leq c_0$, 
\begin{equation*}
T\bigl(Q_{T}(x_0,c_0) \cap \partial_{\varepsilon}\mc{X}\bigr) \subseteq V_{\phi}\bigl(C_0\varepsilon\bigr) \quad\textrm{and}\quad T\bigl(Q_T(x_0,c_0) \cap \mc{X}\bigr) = U_{\phi}(c_0).
\end{equation*}
Here $Q_{T}(x_0,c_0))$ is a (not necessarily coordinate-axis-aligned) cube of side length $c_0)$, centered at $x_0$. Define $v(y) := u(T^{-1}(y))$ for $y \in U_{\phi}(c_0)$. If $u \in C_c^{\infty}(\mc{X})$, then $v \in C_c^{\infty}(U_{\phi}(c_0))$, and moreover $\|v\|_{H^s(U_{\phi}(c_0))}^2 = \|u\|_{H^s(Q_{T}(x_0,c_0) \cap \mc{X})}^2$. Therefore, using the upper bound that we derived in Step 1,
\begin{equation*}
\int_{V_{\phi}(C_0 \cdot \varepsilon)} |v(y)|^2 \,dy \leq C \varepsilon^{2s} \|v\|_{H^s(U_{\phi}(c_0))}^2,
\end{equation*}
we conclude that
\begin{align*}
\int_{Q_{T}(x_0,c_0) \cap \partial_{\varepsilon}\mc{X}} |u(x)|^2 \,dx & = \int_{T(Q_T(x_0,c_0)) \cap \partial_{\varepsilon}\mc{X})} |v(y)|^2 \,dy \\
& \leq \int_{V_{\phi}(C_0 \cdot \varepsilon)} |v(y)|^2 \,dy \\
& \leq C \varepsilon^{2s} \|v\|_{H^s(U_{\phi}(c_0))}^2 = C \varepsilon^{2s} \|u\|_{H^s(Q_{T}(x_0,c_0)) \cap \mc{X})}^2 \leq C \varepsilon^{2s} \|u\|_{H^s(\mc{X})}^2.
\end{align*}

\underline{\textit{Step 3: Lipschitz domain}}.
Finally, we deal with the case where $\mc{X}$ is assumed to be an open, bounded subset of $\Rd$, with Lipschitz boundary. In this case, at every $x_0 \in \partial \mc{X}$, there exists a rigid motion $T_{x_0}: \Rd \to \Rd$ such that $T_{x_0}(x_0) = 0$, a number $c_0(x_0)$, a Lipschitz function $\phi_{x_0}:\Reals^{d - 1} \to [-c_0,c_0]$, and a number $C_0(x_0)$, such that for all $\varepsilon \cdot C_0(x_0) \leq c_0(x_0)$,
\begin{equation*}
T\bigl(Q_{T}(x_0,c_0(x_0)) \cap \partial_{\varepsilon}\mc{X}\bigr) \subseteq V_{\phi}\bigl(C_0(x_0) \cdot \varepsilon\bigr) \quad\textrm{and}\quad T\bigl(Q_T(x_0,c_0(x_0)) \cap \mc{X}\bigr) = U_{\phi}(c_0(x_0)).
\end{equation*}
Therefore for every $x_0 \in \partial \mc{X}$, it follows from the previous step that
\begin{equation*}
\int_{Q_{T_{x_0}}(x_0,c_0(x_0)) \cap \partial_{\varepsilon}\mc{X}} |u(x)|^2 \,dx \leq C(x_0) \varepsilon^{2s} \|u\|_{H^s(\mc{X})}^2,
\end{equation*}
where on the right hand side $C(x_0)$ is a constant that may depend on $x_0$, but not on $u$ or $\varepsilon$.
